---
title: "Akshay - TP dataset"
output: 
  html_notebook:
    code_folding: hide
---

Process the three samples from TP dataset:
- QC on cells
- perform cell-cycle analysis

#### *Load R libraries*
```{r message=FALSE, warning=FALSE}
library(Seurat)
library(Matrix)
library(dplyr)
library(tibble)
library(magrittr)
library(future)
library(RColorBrewer)
library(ggplot2)
```

#### *Set working directory*
```{r message=FALSE, warning=FALSE}
cohort <- 'TP_Compound'
workdir <- '/data/gc-core/taz2008/scRNAseq/scRNAseq_Minkui-Akshay'
sourcedir <- file.path(workdir, 'source', cohort)
figdir <- file.path(workdir, 'figure', cohort)
infodir <- file.path(workdir, 'info', cohort)
```

#### *Load raw UMI counts table*
```{r message=FALSE, warning=FALSE}
# sample info
sample.info <- data.frame(SeqName=c("Wt_MB-231","Negative_MB-231","Active_MB-231_TPO64"), 
                          Name=c("WT","Negative","Active"))
rownames(sample.info) <- c("TP1","TP2","TP3")
print(sample.info)

# load UMI counts matrix
raw.counts.list <- list()
for (k in 1:nrow(sample.info)){
  pid <- rownames(sample.info)[k]
  sid <- sample.info$SeqName[k]
  cat(paste("Loading UMI counts table for", sid, "..."))
  # read counts csv
  counts <- read.csv(file.path(sourcedir,sid,paste0(sid,'_dense.csv')), header=T, check.names=F, stringsAsFactors=F, row.names=1)
  # remove 'CLUSTER' column
  counts <- counts[,-grep('CLUSTER', colnames(counts))]
  # add a prefix to cell id
  rownames(counts) <- paste(pid, rownames(counts), sep='_')
  # transpose and maintain data.frame format
  raw.counts.list[[pid]] <- as.data.frame(t(counts))
  cat(" done.", "\n")
}

# check matrix dimensions
print(sapply(raw.counts.list, FUN=dim))

# merge raw counts matrix
my.MergeMatrix <- function(counts.list){
  cat("Merge raw UMI counts ")
  tfunc <- function(x,y){
    tres <- merge(x, y, by=0, all=T)
    rownames(tres) <- tres$Row.names
    tres <- tres[,-1]
    cat(".")
    return(tres)
  }
  merged.counts <- Reduce(f=tfunc, x=counts.list)
  # fill na with 0
  merged.counts[is.na(merged.counts)] <- 0
  # convert to Matrix
  merged.counts <- as(as.matrix(merged.counts), "dgCMatrix")
  cat(" done.", "\n")
  return(merged.counts)
}

raw.counts.all <- my.MergeMatrix(raw.counts.list)

print(dim(raw.counts.all))
print(table(sapply(colnames(raw.counts.all), FUN=function(x) { strsplit(x,"_")[[1]][1] })))

# free space
rm(raw.counts.list)
gc()
```

#### *Initialize a Seurat object*
```{r message=FALSE, warning=FALSE}
# project name
project <- "akshay"

# pattern for defining mitochondrial/ribosomal genes
mito.pattern <- "^MT-"
ribo.pattern <- "^RPL|^RPS"

# Initialize the Seurat object with the raw (non-normalized data).
panc <- CreateSeuratObject(counts=raw.counts.all, project=project, assay="RNA", min.cells=0, min.features=0, 
                           names.field=1, names.delim="_", meta.data=NULL)

# Calculates the mitochondrial/ribosomal genes per cell
print(paste(length(grep(mito.pattern, rownames(panc), value=T)), "mitochondrial genes detected."))
print(paste(length(grep(ribo.pattern, rownames(panc), value=T)), "ribosomal genes detected."))
panc[["percent.mito"]] <- PercentageFeatureSet(panc, pattern=mito.pattern)
panc[["percent.ribo"]] <- PercentageFeatureSet(panc, pattern=ribo.pattern)

# Add sample condition
tmeta <- data.frame(row.names=rownames(panc@meta.data))
for (tx in colnames(sample.info)){
  tdic <- as.vector(sample.info[,tx])
  names(tdic) <- rownames(sample.info)
  tmeta[,tx] <- as.vector(tdic[as.vector(panc@meta.data[,"orig.ident"])])
}
panc %<>% AddMetaData(metadata=tmeta)

print(panc)
```

#### *QC on cells*
```{r message=FALSE, warning=FALSE}
# violin plot for QC purpose
my.QC.VlnPlot <- function(tobj, tvars=c("nFeature_RNA","nCount_RNA"), tsample_by, tsample_order, tgroup_by=NULL, tgroup_order=NULL, tbounds=NULL, tjitter=T, tncol=2, tlegend=NULL, tjwidth=0.2, talpha=0.3, txsize=12, tlsize=16){
  # get meta data for plotting
  tdata <- FetchData(tobj, c(tsample_by,tvars))
  colnames(tdata) <- c('Sample',tvars)
  tdata$Sample <- factor(tdata$Sample, levels=tsample_order)
  # assign groups if provided
  if (! is.null(tgroup_by)){
    tdata <- tdata %>% rownames_to_column('cellID') %>% 
      left_join(FetchData(tobj, tgroup_by) %>% rownames_to_column('cellID'), by='cellID') %>% column_to_rownames('cellID')
  }
  # reorder cells by group if available
  if (! is.null(tgroup_order)){
    tdata[,tgroup_by] <- factor(tdata[,tgroup_by], levels=tgroup_order)
  }
  # list of plots: one plot per variable
  tplots <- list()
  tk <- 1
  for (tvar in tvars){
    # make plot
    tg <- ggplot(tdata, aes_string(x="Sample", y=tvar))
    if (! is.null(tgroup_by)){
      tg <- ggplot(tdata, aes_string(x="Sample", y=tvar, fill=tgroup_by))
    }
    tg <- tg + geom_violin()
    if(tjitter){
      tg <- tg + geom_jitter(aes_string(color=tgroup_by), shape=16, position=position_jitter(width=tjwidth, height=0), alpha=talpha)
    }
    tg <- tg + stat_summary(fun.data=median_hilow, geom="pointrange", color="gray75")
    if (! is.null(tbounds)){
      if (! is.null(tbounds[[tvar]])){
        tg <- tg + geom_hline(yintercept=tbounds[[tvar]], colour='red', linetype='dotted')
      }
    }
    tg <- tg + ggtitle(tvar)
    tg <- tg + theme_bw()
    tg <- tg + theme(axis.title=element_blank(), axis.text.x=element_text(size=txsize, angle=45, hjust=1, face="bold"))
    tg <- tg + theme(axis.text.y=element_text(size=txsize, face="bold"), plot.title=element_text(size=tlsize, hjust=0.5, face="bold"))
    # add to plot list
    tplots[[tk]] <- tg
    tk <- tk + 1
  }
  # combine plots with Seurat::CombinePlots
  tcombined <- CombinePlots(tplots, ncol=tncol, legend=tlegend)
  return(tcombined)
}

# QC on nFeature_RNA + nCount_RNA + percent.mito
myCellQC <- function(tobj, tfeature.var='nFeature_RNA', tcount.var='nCount_RNA', tmito.var='percent.mito', tsample_by='orig.ident', tsample_order=NULL, tbounds=NULL, talpha=0.5, tptsize=2){
  # orig.ident nCount_RNA nFeature_RNA percent.mito
  tdata <- FetchData(tobj, vars=c(tsample_by,tfeature.var,tcount.var,tmito.var))
  # order samples if provided
  if (! is.null(tsample_order)){
    tdata[,tsample_by] = factor(tdata[,tsample_by], levels=tsample_order)
  }
  colnames(tdata) <- c('Sample',tfeature.var,tcount.var,tmito.var)
  # order data by percent.mito
  tdata <- tdata[with(tdata, order(tdata[,tmito.var])), ]
  # plot
  tg <- ggplot(tdata, aes_string(x=tfeature.var, y=tcount.var, color=tmito.var))
  tg <- tg + geom_point(shape=19, alpha=talpha, size=tptsize)
  tg <- tg + scale_color_gradient(breaks=c(0,25,50,75,100), limits=c(0,100))
  if (! is.null(tbounds)){
    tg <- tg + geom_hline(yintercept=tbounds[[tcount.var]], colour='red', linetype='dotted')
    tg <- tg + geom_vline(xintercept=tbounds[[tfeature.var]], colour='red', linetype='dotted')
  }
  tg <- tg + facet_wrap(~Sample)
  tg <- tg + theme_bw()
  tg <- tg + theme(axis.title=element_text(size=18, color='black'), axis.text=element_text(size=16, color='black'))
  return(tg)
}

# cell numbers before filtering
print('Before filtering:')
print(table(panc$Name))

# pre-filter QC
# violin plot
plot <- my.QC.VlnPlot(tobj=panc, tvars=c("nFeature_RNA", "nCount_RNA", "percent.mito", "percent.ribo"), 
                      tsample_by='Name', tsample_order=c('WT','Negative','Active'), 
                      tgroup_by='Name', tgroup_order=c('WT','Negative','Active'), tbounds=NULL,
                      tjitter=T, tncol=2, tlegend="bottom", tjwidth=0.2, talpha=0.1, txsize=12, tlsize=16)
ggsave(paste(figdir, "QC.Violin.pre-filter.png", sep="/"), width=10, height=8, dpi=600)
# scatter plot
plots <- list()
plots[[1]] <- FeatureScatter(panc, feature1="nFeature_RNA", feature2="nCount_RNA")
plots[[2]] <- FeatureScatter(panc, feature1="nCount_RNA", feature2="percent.mito")
plots[[3]] <- FeatureScatter(panc, feature1="nFeature_RNA", feature2="percent.ribo")
plots[[4]] <- FeatureScatter(panc, feature1="percent.mito", feature2="percent.ribo")
plots.combined <- CombinePlots(plots=plots, ncol=2)
print(plots.combined)
ggsave(paste(figdir, "QC.Scatter.pre-filter.png", sep="/"), width=12, height=10, dpi=600)
# quick QC on nGene X nUMI X percent.mito
plot <- myCellQC(tobj=panc, tfeature.var='nFeature_RNA', tcount.var='nCount_RNA', tmito.var='percent.mito', 
                 tsample_by='Name', tsample_order=c('WT','Negative','Active'),
                 tbounds=NULL, talpha=0.5, tptsize=2)
ggsave(paste(figdir, "QC.Cells.pre-filter.png", sep="/"), plot=plot, width=14.5, height=5, dpi=600)

# filters: nGene > 2000, nGene <= 8000, nUMI > 4000, nUMI <= 90000, percent.mito < 15%
ncells <- nrow(subset(panc@meta.data, nFeature_RNA > 2000 & nFeature_RNA <= 8000 & 
                        nCount_RNA > 4000 & nCount_RNA <= 90000 & percent.mito < 15))
print(paste(round((1 - ncells/ncol(panc))*100, 2), "cells will be removed."))

# re-plot with cutoff labeled in plots
plot <- my.QC.VlnPlot(tobj=panc, tvars=c("nFeature_RNA", "nCount_RNA", "percent.mito", "percent.ribo"), 
                      tsample_by='Name', tsample_order=c('WT','Negative','Active'), 
                      tgroup_by='Name', tgroup_order=c('WT','Negative','Active'), 
                      tbounds=list(nFeature_RNA=c(2000,8000),nCount_RNA=c(4000,90000),percent.mito=c(15),percent.virus=NULL,percent.ribo=NULL),
                      tjitter=T, tncol=2, tlegend="bottom", tjwidth=0.2, talpha=0.1, txsize=12, tlsize=16)
print(plot)
ggsave(paste(figdir, "QC.Violin.pre-filter.with_cutoff.png", sep="/"), width=10, height=8, dpi=600)

plot <- myCellQC(tobj=panc, tfeature.var='nFeature_RNA', tcount.var='nCount_RNA', tmito.var='percent.mito', 
                 tsample_by='Name', tsample_order=c('WT','Negative','Active'),
                 tbounds=list(nFeature_RNA=c(2000,8000),nCount_RNA=c(4000,90000),percent.mito=c(15)), talpha=0.5, tptsize=2)
print(plot)
ggsave(paste(figdir, "QC.Cells.pre-filter.with_cutoff.png", sep="/"), plot=plot, width=14.5, height=5, dpi=600)

# perform cell filtering
# nGene > 2000, nGene <= 8000, nUMI > 4000, nUMI <= 90000, percent.mito < 15%
panc %<>% subset(subset=nFeature_RNA > 2000 & nFeature_RNA <= 8000 & nCount_RNA > 4000 & nCount_RNA <= 90000 & percent.mito < 15)

# cell numbers after filtering
print('After filtering:')
print(table(panc$Name))

# post-filter QC
# violin plot
plot <- my.QC.VlnPlot(tobj=panc, tvars=c("nFeature_RNA", "nCount_RNA", "percent.mito", "percent.ribo"), 
                      tsample_by='Name', tsample_order=c('WT','Negative','Active'), 
                      tgroup_by='Name', tgroup_order=c('WT','Negative','Active'), tbounds=NULL,
                      tjitter=T, tncol=2, tlegend="bottom", tjwidth=0.2, talpha=0.1, txsize=12, tlsize=16)
print(plot)
ggsave(paste(figdir, "QC.Violin.post-filter.png", sep="/"), width=10, height=8, dpi=600)
# scatter plot
plots <- list()
plots[[1]] <- FeatureScatter(panc, feature1="nFeature_RNA", feature2="nCount_RNA")
plots[[2]] <- FeatureScatter(panc, feature1="nCount_RNA", feature2="percent.mito")
plots[[3]] <- FeatureScatter(panc, feature1="nFeature_RNA", feature2="percent.ribo")
plots[[4]] <- FeatureScatter(panc, feature1="percent.mito", feature2="percent.ribo")
plots.combined <- CombinePlots(plots=plots, ncol=2)
print(plots.combined)
ggsave(paste(figdir, "QC.Scatter.post-filter.png", sep="/"), width=12, height=10, dpi=600)
# quick QC on nGene X nUMI X percent.mito
plot <- myCellQC(tobj=panc, tfeature.var='nFeature_RNA', tcount.var='nCount_RNA', tmito.var='percent.mito', 
                 tsample_by='Name', tsample_order=c('WT','Negative','Active'),
                 tbounds=NULL, talpha=0.5, tptsize=2)
print(plot)
ggsave(paste(figdir, "QC.Cells.post-filter.png", sep="/"), plot=plot, width=14.5, height=5, dpi=600)

# free space
rm(plot, plots, plots.combined)
gc()
```

#### *Normalize, Find variable genes, scale data, perform PCA*
```{r message=FALSE, warning=FALSE}
# normalize data
panc %<>% NormalizeData()

# find variable genes
panc %<>% FindVariableFeatures(selection.method="vst", nfeatures=2000)

# scale data
panc %<>% ScaleData()

# highlight the 10 most highly variable genes
top10 <- head(VariableFeatures(panc), 10)
# plot variable features with and without labels
plot1 <- VariableFeaturePlot(panc)
plot2 <- LabelPoints(plot=plot1, points=top10, repel=TRUE)
# Warning: When using repel, set xnudge and ynudge to 0 for optimal results
png(file=paste(figdir, "VariableFeaturePlot.png", sep="/"), width=8000, height=2400, units="px", pointsize=6, res=600)
CombinePlots(plots = list(plot1, plot2))
dev.off()
rm(plot1)
rm(plot2)

# extract the top positive/negative affected genes in one PC
myGetTopPCFeatures <- function(tobj, reduction.name="pca", reduction.key="PC_", pc=1, nfeatures=5){
  # valid assay?
  if (! reduction.name %in% names(tobj)){
    print(paste("Invalid","assay:",reduction.name, sep=" "))
    return(NULL)
  }
  # get values in the given PC
  tvals <- as.vector(tobj[[reduction.name]]@feature.loadings[, paste(reduction.key, pc, sep="")])
  names(tvals) <- rownames(tobj[[reduction.name]]@feature.loadings)
  # order the genes
  tvals.sorted <- sort(tvals)
  # output
  cat("PC_", pc, ":\n", sep="")
  cat(c("Positive:", head(names(rev(tvals.sorted)), nfeatures), "\n"), sep=" ")
  cat(c("Negative:", head(names(tvals.sorted), nfeatures) ,"\n"), sep=" ")
}

# perform PCA
panc %<>% RunPCA()
# use my own function to extract the top positive/negative affected genes in one PC
for (k in 1:10){
  myGetTopPCFeatures(panc, pc=k)
}

# An alternative heuristic method generates an 'Elbow plot':
# a ranking of principle components based on the percentage of variance explained by each one (ElbowPlot function). 
#png(file=file.path(figdir, "PCElbowPlot.png"), width=1600, height=1600, units="px", pointsize=6, res=600)
#ElbowPlot(panc, ndims=30, reduction="pca")
#dev.off()
ElbowPlot(panc, ndims=30, reduction="pca")
```

#### *Assign cell cycle*
```{r message=FALSE, warning=FALSE}
# Assign Cell-Cycle Scores
panc %<>% CellCycleScoring(s.features=cc.genes$s.genes, g2m.features=cc.genes$g2m.genes, set.ident=TRUE)

# how many cells per cell cycle phase?
print('Number of cells per cell cycle phase per sample:')
print(FetchData(panc, vars=c('Name','Phase')) %>% group_by(Name, Phase) %>% summarise_at('Phase', list(counts=length)) 
      %>% group_by(Name) %>% mutate(percent=round(counts/sum(counts)*100,1)))

# Visualize the distribution of cell cycle markers across
RidgePlot(panc, features=c("PCNA", "TOP2A", "MCM6", "MKI67"), ncol=2)

# save Seurat object (initial)
saveRDS(panc, file=file.path(infodir, "panc.rds"))
```

#### *Review cell cycle assignment*
```{r message=FALSE, warning=FALSE}
# minimum & maximum cell cycle scores
print(min(panc@meta.data$S.Score, panc@meta.data$G2M.Score))
print(max(panc@meta.data$S.Score, panc@meta.data$G2M.Score))

# score distribution
print('G2M.Score vs. S.Score')
# G2M v.s. S
plot <- ggplot(panc@meta.data, aes(x=G2M.Score, y=S.Score, color=Phase)) + 
  geom_point(shape=19, size=2, alpha=0.6) + 
  coord_fixed(xlim=c(-0.45,1.35),ylim=c(-0.45,1.35)) + theme_bw()
ggsave(file.path(figdir, 'scatter.G2M.vs.S.png'), plot=plot, width=6, height=5.5, dpi=300)
print(plot)

# G2M
print('G2M.Score')
plot <- ggplot(panc@meta.data, aes(x=G2M.Score)) + geom_histogram(binwidth=0.01) + theme_bw()
ggsave(file.path(figdir, 'histogram.G2M.png'), plot=plot, width=6, height=3.5, dpi=300)
print(plot)

# S
print('S.Score')
plot <- ggplot(panc@meta.data, aes(x=S.Score)) + geom_histogram(binwidth=0.01) + theme_bw()
ggsave(file.path(figdir, 'histogram.G2M.png'), plot=plot, width=6, height=3.5, dpi=300)
print(plot)
```

#### *Dimension reduction and clustering*
```{r message=FALSE, warning=FALSE}
# top PCs for downstream analysis
pcs <- 20

# FindNeighbors: Shared Nearest Neighbor(SNN) Graph Construction
panc %<>% FindNeighbors(reduction="pca", dims=1:pcs)

# FindClusters
panc %<>% FindClusters(resolution=seq(0.05,4,by=0.05), verbose=T)

# dimension reduction using tSNE
panc %<>% RunTSNE(reduction="pca", dims = 1:pcs, seed.use=1, tsne.method="Rtsne", dim.embed=3)
```

#### *check cell compositions per cluster per sample*
```{r message=FALSE, warning=FALSE, fig.width=18, fig.height=15, dpi=300}
# bar plot showing the percentage of cells per cluster in each group, split by clusters
myBarCellCompositionSplit <- function(tobj, tcluster_by='ident', tcluster_order, tgroup_by='Name', tgroup_order=NULL, tcells=NULL, tanncolor=NULL, ttlsize=28, ttxsize=24, tltsize=18, tsxsize=16){
  # calculate percentage of cells per cluster in each group
  tpercent <- FetchData(tobj, vars=c(tgroup_by, tcluster_by), cells=tcells) %>% dplyr::rename('Cluster'=tcluster_by, 'Group'=tgroup_by) %>%
    rownames_to_column('CellID') %>% group_by(Group, Cluster) %>% summarise_at('CellID', length) %>%
    tidyr::complete(Cluster=factor(tcluster_order), fill=list(CellID=0)) %>%
    group_by(Group) %>% mutate_at('CellID', function(x) { round(x/sum(x)*100,2) })
  colnames(tpercent) <- c("Group", "Cluster", "Percent")
  # reorder group/cluster if provided
  if (! is.null(tcluster_order)){
    tpercent$Cluster <- factor(tpercent$Cluster, levels=tcluster_order)
  }
  if (! is.null(tgroup_order)){
    tpercent$Group <- factor(tpercent$Group, levels=tgroup_order)
  }
  # plot
  tg <- ggplot(tpercent, aes(x=Group, y=Percent, fill=Cluster))
  tg <- tg + geom_bar(stat='identity')
  tg <- tg + facet_wrap(~Cluster, scales='free_y')
  if (! is.null(tanncolor)){
    tg <- tg + scale_fill_manual(values=tanncolor)
  }
  tg <- tg + ylab('Percentage of cells')
  tg <- tg + theme_bw()
  tg <- tg + theme(axis.title.x=element_blank(), axis.title.y=element_text(color='black', size=ttlsize))
  tg <- tg + theme(axis.text.x=element_text(color='black', size=ttxsize, angle=60, hjust=1), axis.text.y=element_text(color='black', size=ttxsize))
  tg <- tg + theme(strip.text.x=element_text(color='black', size=tsxsize))
  tg <- tg + theme(legend.text=element_text(size=tltsize), legend.title=element_blank())
  return(tg)
}

# bar plot showing the absolute number of cells per cluster in each group, split by clusters
myBarCellNumberSplit <- function(tobj, tcluster_by='ident', tcluster_order, tgroup_by='Name', tgroup_order=NULL, tcells=NULL, tanncolor=NULL, ttlsize=28, ttxsize=24, tltsize=18, tsxsize=16){
  # calculate absolute number of cells per cluster in each group
  tpercent <- FetchData(tobj, vars=c(tgroup_by, tcluster_by), cells=tcells) %>% dplyr::rename('Cluster'=tcluster_by, 'Group'=tgroup_by) %>%
    rownames_to_column('CellID') %>% group_by(Group, Cluster) %>% summarise_at('CellID', length) %>%
    tidyr::complete(Cluster=factor(tcluster_order), fill=list(CellID=0))
  colnames(tpercent) <- c("Group", "Cluster", "Number")
  # reorder group/cluster if provided
  if (! is.null(tcluster_order)){
    tpercent$Cluster <- factor(tpercent$Cluster, levels=tcluster_order)
  }
  if (! is.null(tgroup_order)){
    tpercent$Group <- factor(tpercent$Group, levels=tgroup_order)
  }
  # plot
  tg <- ggplot(tpercent, aes(x=Group, y=Number, fill=Cluster))
  tg <- tg + geom_bar(stat='identity')
  tg <- tg + facet_wrap(~Cluster, scales='free_y')
  if (! is.null(tanncolor)){
    tg <- tg + scale_fill_manual(values=tanncolor)
  }
  tg <- tg + ylab('Absolute number of cells')
  tg <- tg + theme_bw()
  tg <- tg + theme(axis.title.x=element_blank(), axis.title.y=element_text(color='black', size=ttlsize))
  tg <- tg + theme(axis.text.x=element_text(color='black', size=ttxsize, angle=60, hjust=1), axis.text.y=element_text(color='black', size=ttxsize))
  tg <- tg + theme(strip.text.x=element_text(color='black', size=tsxsize))
  tg <- tg + theme(legend.text=element_text(size=tltsize), legend.title=element_blank())
  return(tg)
}

# set color
my.cluster.color <- c(brewer.pal(12,'Paired'), brewer.pal(8,'Set2'), brewer.pal(9,'Pastel1'), brewer.pal(12,'Set3'))
names(my.cluster.color) <- c(0:40)

my.resolution <- 4
my.numclusters <- length(unique(panc[[paste0('RNA_snn_res.',my.resolution)]][,1]))

# bar plot per sample, separated by clusters
g <- myBarCellCompositionSplit(panc, tcluster_by=paste0('RNA_snn_res.',my.resolution), tcluster_order=0:(my.numclusters-1), tgroup_by='Name', 
                               tgroup_order=c('WT','Negative','Active'), 
                               tcells=NULL, tanncolor=my.cluster.color, ttlsize=20, ttxsize=18, tltsize=16, tsxsize=14)
##ggsave(file.path(figdir, 'percentage.cells.by_sample.split.png'), plot=g, width=20, height=16)
print(g)

# generate bar plot, showing absolute number of cells per cluster in each sample
g <- myBarCellNumberSplit(panc, tcluster_by=paste0('RNA_snn_res.',my.resolution), tcluster_order=0:(my.numclusters-1), tgroup_by='Name', 
                          tgroup_order=c('WT','Negative','Active'), 
                          tcells=NULL, tanncolor=my.cluster.color, ttlsize=20, ttxsize=18, tltsize=16, tsxsize=14)
print(g)
##ggsave(file.path(figdir, 'number.cells.by_sample.split.png'), plot=g, width=20, height=16)

```

#### *R packages information*
```{r message=FALSE, warning=FALSE}
sessionInfo()
```
